DraftOne

### 2016-06-17 DraftOne.Rmd
Get Rmds running on my computer

```{r}
sim_data(n = 3, rr = 1.2, p_exp = .2, lambda = 100)
sim_data(n = 3, rr = 1.02, x_type = "continuous", mu = 10, sd = 10, lambda = 100)
```

@@

```{r}
df <- sim_data(n = 5 * 365, rr = 1.2, p_exp = .2, lambda = 100)
spline_mod(df)
exp(spline_mod(df)[1])

@@

```{r}
df <- sim_data(n = 5 * 365, rr = 1.2, p_exp = .2, lambda = 100)
casecross_mod(df)
exp(casecross_mod(df)[1])

@@

```{r}
df <- sim_data(n = 5 * 365, rr = 1.2, p_exp = .2, lambda = 100)
crossyear_mod(df)
exp(crossyear_mod(df)[1])

>>>>

```{r}
sim_data(n = 3, rr = 1.2, p = .2, lambda = 100)
sim_data(n = 3, rr = 1.02, x_type = "continuous", mu = 10, sd = 10,
         lambda = 100)
```

@@

```{r}
df <- sim_data(n = 5 * 365, rr = 1.2, p = .2, lambda = 100)
spline_mod(df)
exp(spline_mod(df)[1])

@@

```{r}
df <- sim_data(n = 5 * 365, rr = 1.2, p = .2, lambda = 100)
casecross_mod(df)
exp(casecross_mod(df)[1])

@@

```{r}
df <- sim_data(n = 5 * 365, rr = 1.2, p = .2, lambda = 100)
crossyear_mod(df)
exp(crossyear_mod(df)[1])
